\documentclass[11pt]{article}
\usepackage{graphicx}
\begin{document}

\begin{titlepage}
\begin{center}
 prince
\end{center}
 \end{titlepage}
 \tableofcontents
 \newpage
\section{Introduction}\label{sec:intro}
\subsection{Purpose}
 The DCMS is a web application that provides support for managing the services of a small dental clinic.Users will remotely have access to relevant services based on requirements and role.(i.e Dentist,Receptionist,Patients).
\subsection{Scope}
There are four basic users, Dentists, patients, Receptionists and Administrators.All the users have their own profiles in DCMS.
\begin{itemize}

\item 
Dentists can view schedules ,make appointments, give presciptions and view patients health record.
\item 
Patients can make online appointments, they can search for a doctor who specializes on the particular problem they have.Patients can also view their health  records, presciptions, medical expenses and comment on the services provided.
\item 
The receptionist views and manages the appointments, performs day open and close activities. He also sends reports to admin.
\item 
The administrator grants permision to receptionist  and  dentists the authority to view and generates report.He also has the authority to add or delete users. He also provides for the system.
\end{itemize}
\subsection{Definations,Acronyms and Abbreviations}

DCMS
\subsection{References}
\subsection{Overview}
\section{Overall description}
\subsection{Productive perspective}
\subsection{Product functions}
\subsection{user characteristics}
\subsection{Constraints}
\subsection{Assumptions and Dependencies}
 \end{document}
